---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# upim

<!-- badges: start -->
<!-- badges: end -->

This package is a U-statistics based implementation of the Probabilistic Index Models (PIM) proposed by Thas et al. (2012). It supports weighted PIM estimation, which is not implemented in the original authors' {pim} package. It's also more efficient and light-weight.


## Installation

You can install the development version of upim from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ge-li/upim")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(upim)
set.seed(42)
n <- 200
a <- 1
b <- -2
x1 <- rnorm(n)
x2 <- rnorm(n)
# Normal error corresponds to a probit PIM. 
y <- a * x1 + b * x2 + rnorm(n, sd = 1 / sqrt(2))
# Apply some arbitrary monotonic transformation to y.
mono_trans_y = pnorm(plogis(pnorm(y)))^2 + 1 
system.time(obj <- pim_fit(y = mono_trans_y, X = cbind(x1, x2), link = "probit"))
obj$coef
obj$vcov
```

Here is another example of "logit" PIM, and comparing with the \{pim\} package.
The `vcov` estimation is slightly different because \{upim\} uses U-statistics-based
asymptotic sandwich estimator, whereas the \{pim\} package uses the "sparse correlation"
theory based sandwich estimator. They are, however, asymptotically equivalent. 

```{r example2}
# install.packages(c("pim", "evd"))
library(pim)
library(evd)
set.seed(42)
n <- 200
a <- 1
b <- -2
x1 <- rnorm(n)
x2 <- rnorm(n)
# Gumbel error corresponds to a logit PIM. 
y <- a * x1 + b * x2 + rgumbel(n)
# Apply some arbitrary monotonic transformation to y.
mono_trans_y = pnorm(plogis(pnorm(y)))^2 + 1 
# upim 
system.time(upim.obj <- upim::pim_fit(y = mono_trans_y, X = cbind(x1, x2), link = "logit"))
upim.obj$coef
upim.obj$vcov
# pim 
system.time(pim.obj <- pim(mono_trans_y ~ x1 + x2, link = "logit"))
pim.obj@coef
pim.obj@vcov
```
