---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# upim

<!-- badges: start -->
<!-- badges: end -->

This package is a U-statistics based implementation of the Probabilistic Index Models (PIM) proposed by Thas et al. (2012). It supports weighted PIM estimation, which is not implemented in the original authors' {pim} package. It's also more efficient and light-weight.


## Installation

You can install the development version of upim from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ge-li/upim")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(upim)
set.seed(42)
n <- 200
a <- 1
b <- -2
x1 <- rnorm(n)
x2 <- rnorm(n)
y <- a * x1 + b * x2 + rnorm(n, sd = 1 / sqrt(2))
system.time(obj <- pim_fit(y = y, X = cbind(x1, x2), link = "probit"))
obj$coef
obj$vcov
```
